A Simple Model for Small Collections of Magnetic Plasmonic Oligomers

### 2017-05-17 may_paper/draft_2.0.tex
new threemer calculations

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% This is a (brief) model paper using the achemso class
%% The document class accepts keyval options, which should include
%% the target journal and optionally the manuscript type.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[journal=apchd5,manuscript=article]{achemso}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Meta-data block
%% ---------------
%% Each author should be given as a separate \author command.
%%
%% Corresponding authors should have an e-mail given after the author
%% name as an \email command. Phone and fax numbers can be given
%% using \phone and \fax, respectively; this information is optional.
%%
%% The affiliation of authors is given after the authors; each
%% \affiliation command applies to all preceding authors not already
%% assigned an affiliation.
%%
%% The affiliation takes an option argument for the short name.  This
%% will typically be something like "University of Somewhere".
%%
%% The \altaffiliation macro should be used for new address, etc.
%% On the other hand, \alsoaffiliation is used on a per author basis
%% when authors are associated with multiple institutions.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\author{Nicholas P. Montoni}
\author{Steven C. Quillin}
\author{Charles Cherqui}
\affiliation[Department of Chemistry, University of Washington]
{Department of Chemistry, University of Washington, Seattle, WA 98195}
\author{David J. Masiello}
\affiliation[Department of Chemistry, University of Washington]
{Department of Chemistry, University of Washington, Seattle, WA 98195}
\alsoaffiliation[Department of Applied Mathematics, University of Washington]
{Department of Applied Mathematics, University of Washington, Seattle, WA 98195}
\email{masiello@chem.washington.edu}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% The abstract environment will automatically gobble the contents
%% if an abstract is not used by the target journal.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
Ring-like assemblies of metal nanoparticles that exhibit magnetic resonances, called magentic plasmon oligomers, have been of recent interest as negative-index metamaterials. Magnetic plasmon oligomers have potential applications in cloaking, superlensing, information transmission, and sensing. For these reasons, it is imperative to understand the properties of such systems on both small and large scales. We show through theory and simulation that the energy ordering of the magnetic resonances of small oligomers depends greatly on the size and scale of the nanoparticle assembly in ways that purely electric plasmons do not. Following this, we determine the effective pemeability and permittivity of periodic arrays of nanoparticles and show that in certain size regimes they exhibit a negative index of refraction at optical frequencies. As a final exercise, we propose a negative-index material composed of charge tunable semiconductor quantum dots to emphasize the direct control of the optical properties of 2-D magnetic materials.
\end{abstract}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Start the main part of the manuscript here.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
Metal nanoparticles (MNPs) support collective resonances of thier conductions electrons at optical frequencies. These localized surface plasmon resonances (LSPRs) can interact with each other in assemblies of two or more MNPs to produce hybridized resonances of the assembly, much like the hybridization of atomic orbitals in molecules. When these assemblies are arranged in rings, the single LSPRs can give rise to a fictitious, oscillating current which produces an oscillating magnetic dipole inside of the ring. Such systems are known as magnetic plasmon oligomers.

Magnetic plasmon oligomers have been of intense focus due to their potential applications in sensing, lensing, cloaking, and information processing. In a recent paper, Engheta \textit{et al}. state that magnetic systems are well-understood on the single oligomer scale and the nearly infinite scale. [\textbf{CITE Engheta 2017}] However, the properties of collections of few magnetic oligomers have not been fully explored. Much work has been done to elucidate the properties of long chains and large arrays of magnetic oligomers. [\textbf{lots of Halas cites, probably}] The work of Cherqui \textit{et al}. has shown the properties of magnetic systems comprising one, two, and six rings. Furthermore, the dependence of the magnetic properties of the systems on individual nanoparticle geometry, and the relative size of the constituent oligomers has also been determined. This formative work has explained much of the physics behind magnetic plasmons, but it has also raised an interesting problem.

In Cherqui's 2014 work on magnetic plasmons, a quasistatic, electric dipole tight-binding model was used to determine the eigenmodes of the magnetic systems. This model maps each  considered only the electric near-field of the single-particle plasmons and only incorporated nearest-neighbor interactions. For one-ring systems, hereafter called monomers, the lowest energy eigenmode was determined to be the magnetic mode. For the two-ring system, called a twomer, the lowest- and second-lowest-energy modes were determined to be an out-of-phase magnetic mode and an in-phase magnetic mode, respectively. However, in confiring their results with full-wave simulations, they found a discrepancy. While the tight-binding model accurately described the eigenmodes, it inaccurately described their energy-ordering. The simulations placed the in-phase magnetic mode lower in energy than the out-of-phase mode, opposite the ordering of the tight-binding model. An explanation was needed to determine why this result, while counterintuitive, was in fact physical.

The simulations were carried out on very large magnetic oligomers: the constituent particles were hundreds of nanometers across, and the overall oligomers were therefore nearly micron sized. It is well known that in large nanoparticles and over large distances, the quasistatic approximation begins to fail and the intermediate- and far-fields must be considered in order to accurately describe the optical properties. In this paper, we show that this apparent discrepancy is not only expected, but is rectifiable through expanding the tight-binding model to include all inter-particle interactions and the fully retarded electric field. Furthermore, we show that for small, multi-oligomer systems, the size, spacing, and environment greatly impact the eigenspectrum and the ordering of magnetic modes, leading to a high degree of tunability. We show this by building into our model a means to continuously manipulate the scale, interparticle distance, and embedding dielectric constant of each magnetic system. Finally, we recommend ways that this tunability might be enhanced and exploited in future studies.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% OLD INTRO, SAVE FOR CITES %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Bringing two or more metal nanoparticles (MNPs) together allows their individual electric plasmons to hybridize, producing a new set of plasmonic modes\cite{Lucas1976,ARAVIND1981,Xu1995,Mischenko1995}. Plasmon hybridization theory is applied to aggregates of MNPs and explains their collective behavior within the quasistatic limit in which the speed of light is taken to be infinite\cite{NordHal2003,NordProdan2004,Oubre2004,Gomez2009}. Recently, retardation effects on plasmon hybridization have been the focus of study for large particles\cite{Abajo2008,Gu2010} as well as dimers\cite{vonPlessen2007,Rechbacher2003,Kottman2001}, and 2-D arrays\cite{Schatz2003,Royer2005,Chumanov2010} of nanoparticles. Specific arrangements of nanoparticles in 2-D arrays, such as three or more nanoparticles arranged on the vertices of a regular polygon, support a collective mode in which all of the dipole plasmons are oriented head-to-tail. This generates a fictitious, oscillating current loop resulting in an oscillating magnetic dipole moment in the center of the ring\cite{Alu2006,Alu2008,Liu2011,Nord2006,Cherqui2014,Cherqui2016}. These so-called magnetic plasmons are the lowest-energy collective modes of the oligomers and couple to and enhance the magnetic field of incident light\cite{Shalaev2007,Qian2015,Nord2007}, offering a route to applications such as solar cell enhancement\cite{Graydon2011,Alu2014solar,Le2015solar}, biosensing and detection\cite{Zia2010trans,Noginova2008trans,Wang:13,Fan2015,Wei2015,Shvets2012,Altug2012bio,Nord2011fano}, and information storage and propagation\cite{Zhang2006,NordHal2011,NordHal2012}. The rich plasmonic modes of magnetic-plasmon-supporting systems are well-described using plasmon hybridization theory, but when in the quasistatic limit, the energy-order of the modes is not.

Plasmon hybridization theory treats plasmons as point dipoles centered on their associated nanoparticles that interact through dipole-dipole coupling. In the quasistatic limit, these dipoles couple only through time-independent, electric near-field interactions\cite{jackson_classical_1999}, but when the size of and distance between nanoparticles becomes large, this approximation breaks down and intermediate- and far-field effects must be considered, as well as time-delay effects in the near-field\cite{jackson_classical_1999}. The aim of this paper is to incorporate the fully retarded electric field into plasmon hybridization theory and extend studies of retardation effects to magnetic plasmon oligomers. Specifically, we begin by exploring oligomers comprising two and three rings of nanoparticles and compare to full-wave simulation \cite{Hohenester2012} to verify that our approach qualitatively predicts the energy-ordering of the magnetic modes.\cite{Cherqui2014,Cherqui2016}. Following this, we calaculate the coupling betwen individual rings in various oligomers in order to parametrize an effective magnetic-magnetic coupling between magnetic dipoles. Using this new basis, we describe periodic chains and arrays of oligomers.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Back to regularly scheduled programming %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The tight-binding model used in this work maps each electric dipole plasmon onto a harmonic oscillator and allows them to interact through the fully retarded dipole-dipole coupling. The system Hamiltonian is

\begin{equation}
H = \sum_{i}^{n}\frac{\textbf{P}_{i}^{2}}{2m_{\textrm{sp},i}} + \frac{1}{2}m_{\textrm{sp},i}w_{\textrm{sp},i}^2\textbf{X}_{i}^{2} + e^2\sum_{i\neq j}\textbf{X}_i\cdot\boldsymbol{\Lambda}_{ij}\cdot\textbf{X}_j,\label{elec_hammy_1}
\end{equation}

where $\textbf{P}_i$ are the momenta conjugate to the coordinates $\textbf{X}_{i}$, $\omega_{sp,i}$ are the individual LSPR frequencies of each oscillator, $m_{sp,i}$ are the LSPR effective masses and $\boldsymbol{\Lambda}_{ij}$ is the fully retarded dipole-dipole relay tensor (expanded below). To make this Hamiltonian more manageable, it is nondimensionalized using $\textbf{Q}_i = \left(m_{\textrm{sp}}\omega_{\textrm{sp}}/\hbar\right)^{\frac{1}{2}}\textbf{X}_i$ and $\boldsymbol{\Pi}_i = \textbf{P}_i/\sqrt{\hbar m_{\textrm{sp}}\omega_{\textrm{sp}}}$. Substituting into Equation~\ref{elec_hammy_1} and expanding $\boldsymbol{\Lambda}_{ij}$, we get:

\begin{equation}
\begin{aligned}
H = 
\frac{\hbar\omega_{sp}}{2}\sum_{i}^{n}[\boldsymbol{\Pi}_i^2 + \textbf{Q}_i^2] - \frac{\hbar\omega_{sp}}{2}\sum_{i\neq j}\{g_{ij}^{\textrm{NF}}\left[3(\textbf{Q}_i\cdot\hat{\textbf{n}}_{ij})(\hat{\textbf{n}}_{ij}\cdot\textbf{Q}_j) - \textbf{Q}_i\cdot\textbf{Q}_j\right] \\
+ g_{ij}^{\textrm{IF}}\left[3(\textbf{Q}_i\cdot\hat{\textbf{n}}_{ij})(\hat{\textbf{n}}_{ij}\cdot\textbf{Q}_j) -\textbf{Q}_i\cdot\textbf{Q}_j\right] \\ 
- g_{ij}^{\textrm{FF}}\left[(\textbf{Q}_i\cdot\hat{\textbf{n}}_{ij})(\hat{\textbf{n}}_{ij}\cdot\textbf{Q}_j) -\textbf{Q}_i\cdot\textbf{Q}_j\right]\},\label{elec_hammy_2}
\end{aligned}
\end{equation}

In this Hamiltonian we introduce the near, intermediate, and far-field coupling terms: $g_{ij}^{\textrm{NF}} = \frac{\alpha_{sp}}{r_{ij}^3}\cos\left(\frac{\omega r_{ij}}{c}\right)$, $g_{ij}^{\textrm{IF}} = \frac{\alpha_{sp}\omega}{r_{ij}^2 c}\sin\left(\frac{\omega r_{ij}}{c}\right)$, and $g_{ij}^{\textrm{FF}} = \frac{\alpha_{sp}\omega^2}{r_{ij} c^2}\cos\left(\frac{\omega r_{ij}}{c}\right)$, respectively. Additionally, the polarizability $\alpha_{sp} = \frac{e^2}{m_{sp}\omega_{sp}^2}$, $r_{ij}$ is the distance between the ith and jth LSPs, and $\hat{\textbf{n}}_{ij}$ is the unit vector connecting two LSPs. Including these terms, we have incorporated all retardation effects associated with point dipoles\cite{Purcell1973}.

It should be noted that this Hamiltonian, when diagonilzed, results in a transcendental equation. The eigenvalues of the Hamiltonian are functions of $\omega$, which are the frequencies of the collective modes, that is, the eigenvalues are functions of themselves. In order to fully solve this problem, we make a first guess of $\omega$ for a particular mode of interest and iteratively compute the eigenvalues. Using the eigenvalue associated with the mode of interest, the Hamiltonian is diagonalized to convergence. The process is repeated for each mode of interest.

\section{results and discussion}

We explore and manipulate three magnetic oligomer systems in this work: a twomer, a three-ring chain, and three rings arranged in a triangle. In each manipulation, the particles have radius $r_0$ and interparticle spacing $r_{ij}$. In the first set of model calculations, we compare to full-wave simulations to verify that the model accurately captures the properties of the systems, but beyond that we cease comparison to simulation in order to focus on the predictive power of the model. The first calculations, depicted in Figure~\ref{magmodes} show how the magnetic modes of the twomer and threemers are impacted by the overall scale of the system. In these manipulations, the nearest neighbor distances are held at $r_{ij} = 3 \mtimes r_0$ while $r_0$ varies from 1 nm to 30 nm.

In Figure~\ref{magmodes}a, the magnetic mode eigenvalues are computed for each system. The solid lines depict model calculations, and the dashed lines depict simulated results. Interestingly, the magnetic modes exhibit a dynamic energy ordering, switching order twice as a function of scale. It is presumable that they continue to flip at larger and larger sizes. This is confirmed by simulations, with the model overestimating the eigenvalues by about 0.6\% and underestimating the crossing points by under a nanometer. These small errors are consistent across all three systems. Figure~\ref{magmodes}b displays the computed interaction strength for each eigenmode produced by the tight-binding model. In other words, we have plotted $\sum_{i>j}\textbf{p}_{i}\cdot\textbf{E}$ where $\textbf{p}_{i}$ is an eigenvector and $\textbf{E}$ is the field produced by the other dipoles.

\begin{figure}
\centering
\includegraphics[width=.65\paperwidth]{magnetic_mode_eigenvalues_and_interactions.png}
\caption{Magnetic mode eigenvalues (column a), predicted and simulated, and interaction strengths (\
column b) for the magnetic twomer (first row), threemer chain (second row), and threemer ring (thir\
d row). All of the magnetic modes range from ~3.6 eV to ~3.1 eV. In each system, the magnetic modes\
 exhibit multiple crossings, showing that the eigenspectrum of these magnetic systems depends on th\
eir scale. The model consistently overestimates the eigenvalues by 0.5 eV, and consistently underes\
timates the crossing points by less than a nanometer. The twomer has two magnetic modes, one in-pha\
se mode (blue trace) and one out-of-phase mode (orange trace). The threemer chain has three modes, \
an in-phase mode (blue trace), a minimally out-of-phase mode (orange trace), and a maximally out-of\
-phase mode (green trace). The threemer ring exhibits three magnetic modes, but the out-of-phase mo\
des (orange trace) are degenerate so only one is depicted. The other mode is a maximally in-phase m\
ode (blue trace). To further emphasize the impact of scale, we have plotted the total interaction s\
trength of each eigenmode, \textit{i.e.} the sum of each eigenvector's dot product with the electri\
c field of all of the other dipoles. This calculation reaffirms the scale dependence and predicts m\
ode crossings at the same scale as both the eigenvalue calculation and the simulations.}
\label{fig:magmodes}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=.65\paperwidth]{dielectric_study.png}
\caption{Magnetic mode eigenvalues for twomers (first row), threemer chains (second row), and threemer rings (third row) with particle sizes of 15 nm (column a) and 30 nm (column b) as a func
tion of the dielectric constant of an embedding medium. As the dielectric constant is increased from 1 to 3, the magnetic mode splitting decreases and the overall energy decreases. At very hi
gh dielectric values, the magnetic mode eigenvalues converge to the single particle resonance frequency. This can be explained by the increasing opacity of the medium effectively screening in
ter-particle interactions. It is also important to note that between $\varepsilon_b = 1$ and $\varepsilon_b = 1.5$, the magnetic modes flip order. Thus, the increasing opacity of the medium e
ffectively decreases the scale of the system.}
\label{fig:dielectric}
\end{figure}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% This is a (brief) model paper using the achemso class
%% The document class accepts keyval options, which should include
%% the target journal and optionally the manuscript type.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[journal=ancac3,manuscript=article]{achemso}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Meta-data block
%% ---------------
%% Each author should be given as a separate \author command.
%%
%% Corresponding authors should have an e-mail given after the author
%% name as an \email command. Phone and fax numbers can be given
%% using \phone and \fax, respectively; this information is optional.
%%
%% The affiliation of authors is given after the authors; each
%% \affiliation command applies to all preceding authors not already
%% assigned an affiliation.
%%
%% The affiliation takes an option argument for the short name.  This
%% will typically be something like "University of Somewhere".
%%
%% The \altaffiliation macro should be used for new address, etc.
%% On the other hand, \alsoaffiliation is used on a per author basis
%% when authors are associated with multiple institutions.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\author{Nicholas P. Montoni}
\author{Steven C. Quillin}
\author{Charles Cherqui}
\author{David J. Masiello}
\affiliation[Department of Chemistry, University of Washington]
{Department of Chemistry, University of Washington, Seattle, WA 98195}
\email{masiello@chem.washington.edu}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% The abstract environment will automatically gobble the contents
%% if an abstract is not used by the target journal.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
Ring-like assemblies of metal nanoparticles that exhibit magnetic resonances, called magnetic plasmon oligomers, have been of recent interest as negative-index metamaterials and light-harvesting devices. For these reasons, it is imperative to understand the properties of such systems on the single- to few-oligomer scale. We show through theory and simulation that the energy ordering of the magnetic resonances of few-oligomer systems depends on size, scale, and environment in ways that purely electric plasmons do not. We show that the dynamic ordering of the eigenmodes of magnetic systems is due entirely to retardation effects and can be understood by inspecting the intermediate- and far-field contributions which are excluded in the quasistatic approximation. We highlight the versatility and tunability of magnetic plasmon oligomers, elucidating a previously unexplored physical phenomenon and suggesting future applications of magnetic plasmons in highly sensitive detection methods. 
\end{abstract}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Start the main part of the manuscript here.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
Metal nanoparticles (MNPs) support collective resonances of their conduction electrons at optical frequencies. These localized surface plasmon resonances (LSPRs) can interact with each other in assemblies to produce hybridized resonances, much like the hybridization of atomic orbitals in molecules\cite{Lucas1976,ARAVIND1981,Xu1995,Mischenko1995}. When these MNPs are arranged in rings, the single LSPRs can give rise to a collective mode that produces an oscillating magnetic dipole in he center of the ring\cite{Alu2006,Alu2008,Liu2011,Nord2006,Cherqui2014,Cherqui2016}. Such systems are known as magnetic plasmon oligomers and have been of intense focus due to their potential applications in sensing\cite{Zia2010trans,Noginova2008trans,Wang:13,Fan2015,Wei2015,Shvets2012,Altug2012bio,Nord2011fano}, lensing, cloaking, and information processing\cite{Zhang2006,NordHal2011,NordHal2012}. In Cherqui's 2014 work on magnetic plasmons, a quasistatic, electric dipole tight-binding model was used to describe the magnetic systems\cite{Cherqui2014}; we adapt this model to expand on the results of that work. The original model considered only the electric near-field of the single-particle plasmons and only incorporated nearest-neighbor interactions. As a result, while it accurately predicted the nature of the magnetic eigenmodes, it inaccurately described their energy ordering as confirmed by simulation. An explanation was needed to determine why the tight-binding model would predict different energy-ordering than full-wave simulations.

In a recent paper, Engheta \textit{et al}. state that magnetic systems are well-understood on the single oligomer scale and the nearly infinite scale\cite{Engheta2017}. Furthermore, the dependence of magnetic properties on individual nanoparticle geometry and the relative size of the constituent oligomers has also been determined\cite{Cherqui2016}. However, the properties of few-oligomer systems have not been fully explored. Here we show that to fully understand the properties of magnetic oligomers on the few-oligomer scale, the simple tight-binding model described above must be extended to include both the fully-retarded electric fields and all inter-particle interactions. We show this through three explorations of oligomer properties: system size, dielectric constant of the environment, and inter-particle spacing, and we confirm our results using full-wave simulations\cite{Hohenester2012}.

It is well-known that as MNPs and aggregates become larger, the quasistatic approximation breaks down. There has been much work done to elucidate the effects of retardation on large MNPs\cite{Abajo2008,Gu2010}, dimers\cite{vonPlessen2007,Rechbacher2003,Kottman2001}, and extended 2-D arrays of particles\cite{Schatz2003,Royer2005,Chumanov2010}. Magnetic oligomers composed of two or more rings of particles have the potential to be hundreds of nanometers to microns across, justifying the need to consider retardation effects in determining their optical properties. In order to incorporate retardation effects into quasistatic plasmon hybridization theory, we begin by mapping the dipole plasmon of each MNP onto a set of harmonic oscillators, and allow them to couple through their electric fields according to the following Hamiltonian:

\begin{equation}
H = \sum_{i}^{n}\frac{\textbf{P}_{i}^{2}}{2m_{\textrm{sp},i}} + \frac{1}{2}m_{\textrm{sp},i}\omega_{\textrm{sp},i}^2\textbf{X}_{i}^{2} - e^2\sum_{i\neq j}\textbf{X}_i\cdot\boldsymbol{\Lambda}_{ij}\cdot\textbf{X}_j,\label{elec_hammy_1}
\end{equation}

where $\textbf{P}_i$ are the momenta conjugate to the plasmon coordinates $\textbf{X}_{i}$, $\omega_{\textrm{sp},i}$ are the individual LSPR frequencies of each oscillator, $m_{\textrm{sp},i}$ are the LSPR effective masses and $\boldsymbol{\Lambda}_{ij}$ is the fully retarded dipole-dipole relay tensor (expanded below)\cite{jackson_classical_1999}. To make this Hamiltonian more manageable, it is nondimensionalized using $\textbf{Q}_i = \left(m_{\textrm{sp}}\omega_{\textrm{sp}}/\hbar\right)^{\frac{1}{2}}\textbf{X}_i$ and $\boldsymbol{\Pi}_i = \textbf{P}_i/\sqrt{\hbar m_{\textrm{sp}}\omega_{\textrm{sp}}}$. Substituting into Equation~\ref{elec_hammy_1} and expanding $\boldsymbol{\Lambda}_{ij}$, we get:

\begin{equation}
\begin{aligned}
H = 
\frac{\hbar\omega_{sp}}{2}\sum_{i}^{n}[\boldsymbol{\Pi}_i^2 + \textbf{Q}_i^2] - \frac{\hbar\omega_{sp}}{2\varepsilon_b}\sum_{i\neq j}\{g_{ij}^{\textrm{NF}}\left[3(\textbf{Q}_i\cdot\hat{\textbf{n}}_{ij})(\hat{\textbf{n}}_{ij}\cdot\textbf{Q}_j) - \textbf{Q}_i\cdot\textbf{Q}_j\right] \\
+ g_{ij}^{\textrm{IF}}\left[3(\textbf{Q}_i\cdot\hat{\textbf{n}}_{ij})(\hat{\textbf{n}}_{ij}\cdot\textbf{Q}_j) -\textbf{Q}_i\cdot\textbf{Q}_j\right] \\ 
- g_{ij}^{\textrm{FF}}\left[(\textbf{Q}_i\cdot\hat{\textbf{n}}_{ij})(\hat{\textbf{n}}_{ij}\cdot\textbf{Q}_j) -\textbf{Q}_i\cdot\textbf{Q}_j\right]\},\label{elec_hammy_2}
\end{aligned}
\end{equation}

In this Hamiltonian we introduce the near, intermediate, and far-field coupling terms: $g_{ij}^{\textrm{NF}} = \frac{\alpha_{sp}'}{r_{ij}^3}\cos\left(k r_{ij}\right)$, $g_{ij}^{\textrm{IF}} = \frac{\alpha_{sp}'k}{r_{ij}^2}\sin\left(k r_{ij}\right)$, and $g_{ij}^{\textrm{FF}} = \frac{\alpha_{sp}'k^2}{r_{ij}}\cos\left(k r_{ij}\right)$, respectively, with wavenumber $k = \sqrt{\varepsilon_b}\frac{\omega}{c}$. Additionally, $r_{ij}$ is the distance between the ith and jth LSPRs and $\hat{\textbf{n}}_{ij}$ is the unit vector connecting two LSPRs. We further incorporate retardation effects by considering the lattice dispersion in the polarizability $\alpha_{sp}' = \left(\alpha_{sp}^{-1} - i\frac{2}{3}k^3\right)^{-1}$ with $\alpha_{sp} = r_0^3\frac{3}{\varepsilon_{\infty}-2\varepsilon_b}$. Including these terms, we have incorporated all retardation effects associated with point dipoles\cite{Purcell1973,Draine1993}.

It should be noted that this Hamiltonian, when diagonalized, results in a transcendental equation whose solutions, the eigenvalues $\omega$, are functions of themselves. In order to fully solve this problem, we make a first guess of $\omega$ for a particular mode of interest and iteratively compute the eigenvalues. Using the eigenvalue associated with the mode of interest, the Hamiltonian is diagonalized to convergence. The process is repeated for each mode of interest.

\section{Results and Discussion}

In this work, we model silver nanoparticles using a Drude model with $\omega_p = 9.1$ eV, $\varepsilon_{\infty} = 3.77$, and $\gamma = 0.003$ eV. Note that we have greatly reduced the damping constant in order to better resolve the magnetic modes in the simulations. The oligomer unit cell is a six-member ring, with silver nanoparticles located at the vertices of a regular hexagon. We explore and manipulate three magnetic oligomer systems: a twomer, a linear threemer, and a triangular threemer. The number of rings in a magnetic system corresponds to the number of magnetic modes in the system\cite{Cherqui2014}. The twomer supports an in-phase mode (North-North, or NN) and an out-of-phase mode (North-South, or NS). The linear threemer supports an all in-phase mode (North-North-North, or NNN), a minimally out-of-phase mode (North-Zero-South, or NZS), and a maximally out-of-phase mode (North-South-North, or NSN). The triangular threemer supports an all in-phase mode (North-North-North, or NNN) and two degenerate out-of-phase modes (North-South, or NS). These modes and their relative magnetic fields are depicted in Figures~\ref{magmodes},~\ref{dielectric}, and ~\ref{spacing}. In each manipulation, the particles have radius $r_0$ and nearest-neighbor spacing $r_{\textrm{nn}}$. In the first set of model calculations, we compare to full-wave simulations to verify that the model accurately captures the properties of the systems, but beyond that we cease comparison to simulation in order to focus on the predictive power of the model. The first calculations, depicted in Figure~\ref{magmodes} show how the magnetic modes of the twomer and threemers are impacted by the overall scale of the system. In these manipulations, the nearest neighbor distances are held at $r_{\textrm{nn}} = 3 \times r_0$ while $r_0$ varies from 1 nm to 30 nm.

\begin{figure}
\centering
\includegraphics[width=.6\paperwidth]{magnetic_mode_eigenvalues_and_interactions.png}
\caption{Magnetic mode eigenvalues (column a), predicted and simulated, and interaction strengths (column b) for the magnetic twomer (first row), linear threemer (second row), and triangular threemer (third row). All of the magnetic modes range from 3.6 eV to 3.1 eV. In each system, the magnetic modes exhibit multiple crossings, showing that the eigenspectrum of these magnetic systems depends on their scale. The model consistently overestimates the eigenvalues by 0.05 eV, and consistently underestimates the crossing points by less than a nanometer. To further emphasize the impact of scale, we have plotted the total interaction strength of each eigenmode, \textit{i.e.} the sum of each eigenvector's dot product with the electric field of all of the other dipoles. This calculation reaffirms the scale-dependence and predicts the same mode crossings as both the eigenvalue calculation and the simulations.}
\label{magmodes}
\end{figure}

In Figure~\ref{magmodes}a, the magnetic mode eigenvalues are computed for each system. The solid lines depict model calculations, and the dashed lines depict simulated results. Interestingly, the magnetic modes exhibit a dynamic energy ordering, switching order twice as a function of scale. It is presumable that they continue to flip at larger and larger sizes. This is confirmed by simulations, with the model overestimating the eigenvalues by about 0.05 eV and underestimating the crossing points by under a nanometer. These small errors are consistent across all three systems. Figure~\ref{magmodes}b displays the computed interaction strength for each eigenmode produced by the tight-binding model,

\begin{equation}
\begin{aligned}
U_{\textrm{int}} = -$\sum_{i>j}\textbf{p}_{i}\cdot\textbf{E}$
\label{interactionenergy}
\end{aligned}
\end{equation}

where $\textbf{p}_{i}$ is an eigenvector and $\textbf{E}$ is the field produced by the other dipoles. This calculation serves as a further confirmation of the mode-switching, as the interaction strengths follow the eigenvalues.

\begin{figure}
\centering
\includegraphics[width=0.6\paperwidth]{dimer_interaction.png}
\caption{Relative interaction strengths for the four possible dipole arrangements of a nanoparticle dimer: collinear (a), parallel (b), anti-collinear (c), and anti-parallel (d). Plotted are the near-field (blue), intermediate-field (orange), far-field (green), and total (black, dashed) interaction strengths for each set of dipoles as a function of dipole-dipole distance. Interestingly, and stemming from the form of the dipole relay tensor, the far-field interaction term is zero for both pairs of linear dipoles. From these plots, it can be seen that the favorability of a specific dipole arrangement depends on the separation between the dipoles. This can be seen in the fact that each part of the field depends differently on the separation, and each field term contains an oscillating term. At short length scales, the interaction is dominated by the near-field. However, as the distance increases, the interaction is dominated by the intermediate field (a and c) or the far-field (b and d). As a result, there are separation distances at which normally unfavorable arrangements become favorable. Since magnetic oligomers can be described through pairwise interactions of electric dipoles, it follows that the eigenvalues must also change order as different arrangements of electric dipoles become more and less favorable.}
\label{dimers}
\end{figure}

To gain an explanation for this mode-switching phenomenon, we investigate the fully retarded electric field. In Figure~\ref{dimers} we plot the near-, intermediate-, far-field, and total interaction strength as a function of MNP separation for the four possible arrangements of dipoles. There are two overall trends. At small distances, the overall interaction is dominated by the near-field term due to its $\frac{1}{r_{ij}^3}$ dependence. At larger distances, the overall interaction follows the intermediate-field (Figure~\ref{dimers}a and c) or the far-field (Figure~\ref{dimers}b and d). The second trend is the changing sign of the three field terms and the total interaction. This distance-dependent oscillatory nature determines the energy-ordering of pairs of dipoles, and thus influences the size-dependence of the eigenmode order in amgnetic oligomers. In fact, it has been well documented that system length-scale has an oscillatory impact on its eigenenergies\cite{vonPlessen2007,Pinchuk2016} For example, at some length scales, the dipole-dipole interactions in the North-South mode of the twomer are more favorable than those in the North-North mode, but this favorability changes as a function of system size.

We have convinced ourselves that 1) the quasistatic, nearest-neighbors tight-binding model does not contain enough information to agree with fully retarded electrodynamics simulations, 2) those same simulations conforn to the results from an updated tight-binding model that incorporates retardation effects and all-particle interactions and 3) the unexpected mode switching exhibited by these magnetic systems is entirely physical and explicable by the varying, distance-dependent decay and oscillation of the electric field terms. With a working model and a basic physical understanding of these three systems, we now perform a series of computations to look at its tunable properties. In the previous section, the scale of the systems was changed. However, this would be impossible to manipulate in a laboratory. We focus on properties with experimental analogues, namely, the dielectric constant of the embedding medium and the nearest-neighbor spacing between nanoparticles.

\begin{figure}
\centering
\includegraphics[width=.6\paperwidth]{dielectric_study.png}
\caption{Magnetic mode eigenvalues (column a) for the twomer (first row), linear threemer (second row), and triangular threemer (third row) with particle sizes of 20 nm and magnetic mode eigenvalue differences (column b) as a function of the dielectric constant of an embedding medium. As the dielectric constant is increased from 1 to 3, the magnetic mode splitting approaches zero and the overall energy decreases. At very high dielectric values, the magnetic mode eigenvalues converge to the single particle resonance frequency. This is the result of the dielectric constant reducing the inter-particle interactions. It is also important to note that between $\varepsilon_b = 1$ and $\varepsilon_b = 1.5$, the magnetic mode differences vary sharply, either becoming much more positive or much more negative. This is indicative of mode-switching that is difficult to see in the eigenvalue plots. The increasing dielectric constant has a similar effect to increasing the scale of the system, as it recovers the same energy ordering for $r_0 > 20$ nm.}
\label{dielectric}
\end{figure}
